Project Notes

### 2020-04-06 notes/notes.tex
Notes: update 06/04/2020

>>>>

\paragraph{06/04/2020}
\begin{itemize}
\item
Modified Node.js code generation templates to
take inspiration from the browser ones -- namely,
to make the runtime more lightweight by pushing
logic to the individual states; again, this means
no more huge switch statement with duplication.

\item
New structure for Node.js generated code generally
works. Explicitly used partial application to
focus the types (e.g. State $\to$ ReceiveState $\to$
ReceiveState.S12), and define each non-terminal
state as a separate module to internally use
its known message/label types to parse messages
without having one large switch statement in the
runtime.

\item
Taking cues from Express middleware (with
the \texttt{next} function) to allow the
runtime to pass the send and receive functions
into the individual states, and give a callback
function for the individual states to pass any
data back to the runtime.

\item
An example of this is for receive states -- 
the receive state needs to construct the message 
receive handler \textbf{tailored to the types/labels of 
that particular state}. This message receive handler
will do the parsing, invoke the correct receive
function, and advance the EFSM to the correct
successor state (achieved by having the runtime
pass the state-advancing function as param).

\item
Problem -- still need a type cast for the time being
with the handler functions; not sure why the types
aren't specific enough , trying to make sense of the 
error message at the moment.
\end{itemize}
